MSOA domestic Electricty and Gas maps

### 2021-08-09 MSOA domestic Elec and Gas.Rmd
Changed so the first column of 2010 electricty data is skipped

```{r Mapping the electrcity consumption of the MSOAs}
msoa_elecData$MSOA11CD <- msoa_elecData$ 'Middle Layer Super Output Area (MSOA) Code' #Creating a variable with the LA code and the name as in the sf_data
msoa_merged_sf <-merge(msoa_sf_data, msoa_elecData)
ggplot2::ggplot(msoa_merged_sf) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
```
####Mapping the change from 2010 to 2019
```{r Creating the difference in MSOA mean dom elec consumption variable}
domelec_MSOA_2010<-readr::read_csv(paste0(dataFolder,"energy/electricity/MSOA Dom Elec csv/MSOA_DOM_ELEC_2010.csv"))
domelec_MSOA_2019<-readr::read_csv(paste0(dataFolder, "energy/electricity/MSOA Dom Elec csv/MSOA_DOM_ELEC_2019.csv"))
domelec_MSOA_2010$domelec2010<-domelec_MSOA_2010$'Mean consumption (kWh per meter)'
domelec_MSOA_2019$domelec2019<-domelec_MSOA_2019$'Mean consumption (kWh per meter)'
merged_domelec<-merge(domelec_MSOA_2010, domelec_MSOA_2019, by="Middle Layer Super Output Area (MSOA) Code", all=TRUE)
names(merged_domelec)
merged_domelec$domelec_diff<-merged_domelec$domelec2019 - merged_domelec$domelec2010
summary(merged_domelec)
```
```{r Mapping the MSOA difference in mean dom elec consumption}
merged_domelec$MSOA11CD<-merged_domelec$"Middle Layer Super Output Area (MSOA) Code"
msoa_domelec20102019<-merge(msoa_sf_data, merged_domelec)
ggplot2::ggplot(msoa_domelec20102019)+geom_sf(aes(fill=domelec_diff))+scale_fill_continuous(name="Change in Mean comsumpton (kWh per meter)",low="green",high="red")+labs(caption="Solent(all MSOAs)")
```
### Mapping the Gas
####2019
```{r Loading in the MSOA gas consumption data}
# gas consumption data at MSOA level (pre downloaded)
inFile <-paste0(dataFolder, "energy/gas/MSOA Dom Gas csv/MSOA_GAS_2019.csv")
msoa_gasData <- readr::read_csv(inFile)
head(msoa_gasData)
```
```{r Mapping the gas consumption of the MSOAs}
msoa_gasData$MSOA11CD <- msoa_gasData$ 'Middle Layer Super Output Area (MSOA) Code' 
msoa_merged_sf_domgas <-merge(msoa_sf_data, msoa_gasData)
ggplot2::ggplot(msoa_merged_sf_domgas) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
```
> Does this match to non-gas areas??

>>>>

```{r Mapping the electrcity consumption of the MSOAs}
msoa_elecData$MSOA11CD <- msoa_elecData$ 'Middle Layer Super Output Area (MSOA) Code' #Creating a variable with the LA code and the name as in the sf_data
msoa_merged_sf <-merge(msoa_sf_data, msoa_elecData)
ggplot2::ggplot(msoa_merged_sf) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
```
####Mapping the change from 2010 to 2019
```{r Creating the difference in MSOA mean dom elec consumption variable}
domelec_MSOA_2010<-readr::read_csv(paste0(dataFolder,"energy/electricity/MSOA Dom Elec csv/MSOA_DOM_ELEC_2010.csv"),skip = 1)
domelec_MSOA_2019<-readr::read_csv(paste0(dataFolder, "energy/electricity/MSOA Dom Elec csv/MSOA_DOM_ELEC_2019.csv"))
domelec_MSOA_2010$domelec2010<-domelec_MSOA_2010$'Mean consumption (kWh per meter)'
domelec_MSOA_2019$domelec2019<-domelec_MSOA_2019$'Mean consumption (kWh per meter)'
merged_domelec<-merge(domelec_MSOA_2010, domelec_MSOA_2019, by="Middle Layer Super Output Area (MSOA) Code", all=TRUE)
names(merged_domelec)
merged_domelec$domelec_diff<-merged_domelec$domelec2019 - merged_domelec$domelec2010
summary(merged_domelec)
```
```{r Mapping the MSOA difference in mean dom elec consumption}
merged_domelec$MSOA11CD<-merged_domelec$"Middle Layer Super Output Area (MSOA) Code"
msoa_domelec20102019<-merge(msoa_sf_data, merged_domelec)
ggplot2::ggplot(msoa_domelec20102019)+geom_sf(aes(fill=domelec_diff))+scale_fill_continuous(name="Change in Mean comsumpton (kWh per meter)",low="green",high="red")+labs(caption="Solent(all MSOAs)")
```
### Mapping the Gas
####2019
```{r Loading in the MSOA gas consumption data}
# gas consumption data at MSOA level (pre downloaded)
inFile <-paste0(dataFolder, "energy/gas/MSOA Dom Gas csv/MSOA_GAS_2019.csv")
msoa_gasData <- readr::read_csv(inFile)
head(msoa_gasData)
```
```{r Mapping the gas consumption of the MSOAs}
msoa_gasData$MSOA11CD <- msoa_gasData$ 'Middle Layer Super Output Area (MSOA) Code' 
msoa_merged_sf_domgas <-merge(msoa_sf_data, msoa_gasData)
ggplot2::ggplot(msoa_merged_sf_domgas) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
```
> Does this match to non-gas areas??
